logit

### 2021-12-01 logit.Rmd
Ran logistic model

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(glmnet)
```

```{r}
train <- read.csv("train.csv")
test <- read.csv("test.csv")

model_glm = glm(HeartDisease ~ ., data = train, family = "binomial")

summary(model_glm)
```

```{r}
predicted2 <- predict(model_glm, newdata = test, "response")

predicted2 <- ifelse(predicted2>0.5,1,0)

confm2<-table(predicted=predicted2,True=test$HeartDisease)
confm2
paste("the overall fraction of correct predictions in the test dataset is :",(confm2[1,1]+confm2[2,2])/sum(confm2))
```
